Species motif participation provides unique information about species risk of extinction

### 2023-04-18 manuscript/JAE_reply.tex
Updates from Overleaf

                \textbf{R:}
            The sentence the reviewer refer to is "How disturbances such as population decline or extinction lead to the loss of species via  direct and indirect effects (i.e., secondary extinctions) has long been a vibrant area of research (Curtsdotter et al., 2011a; Dunne & Williams, 2009; Ekl ̈of & Ebenman, 2006 Santos et al., 2021) " Here

>>>>

                \textbf{R:}
            The sentence the reviewer refer to is "How disturbances such as population decline or extinction lead to the loss of species via  direct and indirect effects (i.e., secondary extinctions) has long been a vibrant area of research (Curtsdotter et al., 2011a; Dunne & Williams, 2009; Eklöf & Ebenman, 2006 Santos et al., 2021)." We can understand the reviewer´s confusion, but in fact species extinctions are both the disturbance and the response; an initial extinction of a species (the primary e
